---
title: "R Markdown and Leaflet"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Manoli Heyneke"
date: "12/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)

```

```{r}
library(leaflet)
library(readr)
```

```{r}
df<-read_csv("shared_car_loc.csv")
```


## Context
In order to reduce the number of owned cars, the city of Tel Aviv launched a shared-car project, called AutoTel. Users of the service are able to reserve a car using a mobile app, and pay for it by the minute. The project that was launched in October 2017 attracted over 7500 users, with more than 50% of them using the service at least once a week.

I obtained the data from the following kaggle page [https://www.kaggle.com/gidutz/autotel-shared-car-locations](https://www.kaggle.com/gidutz/autotel-shared-car-locations)


## The Map
I made use of the clustering plugin that Leaflet provides due to the large amount of markers on the map as well as the
Leaflet measuring plugin which you can play around with and measure the the distance between points aswell as the area 
of connected points.


### April 12, 2021
```{r}
df%>%
        leaflet()%>%
        addTiles()%>%
        fitBounds(34.762,32.045,34.825,32.121) %>%
        addMeasure()%>%
        addMarkers(~longitude,~latitude,
                   clusterOptions = markerClusterOptions())
```
















